---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# Solving and simulating a class of LRE models {-}

This package solves for the recursive representation of the stable solution to a system of linear difference equations. Currently, this is done only for the autonomous case with the assumption of no exogenous shocks. 

Inputs are two square matrices E and A and a natural number n where E and A are the coefficient matrices of the difference equation Ex(t+1) = Ax(t). 

The output of the package are (currently) two functions g and h for the decision rule and the law of motion respectively.

To install run:

```{r, eval = FALSE}
devtools::install_github("nuritovbek/lrem")
```
To use the package, call the lre_auto function with the coefficient matrices of your model and a number of predetermined variables in n:

```{r, eval=F}
library(lrem)
lre_auto(A, E, n)
```



```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

